Air cargo load and route planning in pickup and delivery operations

### 2024-01-27 latex/eswa.tex
Brazil figura changed

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{brazil.png}
	\caption{ {\it Shims/GA} best tour (may not be optimal)}
	\label{fig:brazil}
\end{figure}
}

>>>>

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{brazil.png}
	\caption{ {\it Shims/GA} best tour (may not be optimal)}
	\label{fig:brazil}
\end{figure}

The airports cited in Figure \ref{fig:brazil} are: São Paulo (GRU), Congonhas (CGH), Curitiba (CWB), Porto Alegre (POA), Florianópolis (FLN),  Vitória (VIX), Salvador (SSA), Recife (REC), Fortaleza (FOR), Belém (BEL), Manaus (MAO), Brasília (BSB), Goiânia (GYN), Confins (CNF), and Rio de Janeiro (GIG), returning to GRU.
